Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-15 tex/MesnardoBarba2019.tex
add note on reviewer contributions

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their suggestions.

>>>>

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
We would like to thank Kenji Takeda, Fred Park, and Joshua Poulson of Microsoft for their help.
We are also immensely grateful to the reviewers, Patrick O'Leary \cite{oleary_2019} and Freddie Witherden \cite{witherden_2019}, for their contributions, which helped make the paper's audience and purpose more clear, in addition to other improvements.
We include our detailed replies to the reviewer suggestions as a markdown file in the GitHub repository for this paper (exported from GitHub issues).
